Similar Sentence Detection Using Locality Sensitive Hashing Technique on Wikipedia

### 2013-11-04 article/article-draft.tex
Removing cluster size limit

\documentclass{acm_proc_article-sp}
\usepackage{url}
\usepackage{algpseudocode}
\usepackage{verbatim}
\usepackage{microtype}
\usepackage{enumerate}
\usepackage{enumitem}
\usepackage{epsfig}
\usepackage{algorithmicx}
\usepackage{algorithm}
\usepackage{natbib}

\begin{document}

@@

Based on our preliminary analysis, templatification tends to occur most often between articles that maintain large lists of information related to the same general sub-theme of different topics. For example, of the top 10 pairs of articles with the highest similarity count, one article pair was the articles titled ''List of birds of Zambia'' and ''List of birds of Tanzania''. With both countries sharing the same geographic region, it is not unexpected that their respective wikipedia articles on the countrys' bird species would be highly comparable. For clarity purposes, we define \emph{similarity count} as simply the total number of sentences between two articles that were found to share the same hash signature. Using the output of the minhashing routine, we performed a pairwise similarity count across all articles that shared similar sentences. Overall, we found $\approx 6500$ wikipedia article pairs that had a similarity count greater than $50$.

@@

\begin{table}
\centering
\caption{Top 10 Article Pair Titles}
\begin{tabular}{| l | c |}
    \hline
    \textbf{Article ID} & \textbf{Title} \\ \hline
    21986867 & 2000 New Year Honours \\ \hline
    21986897 & 1999 New Year Honours \\ \hline
    3951586 & Instruments of the United Kingdom, 1994 \\ \hline
    3951664 & Instruments of the United Kingdom, 1995 \\ \hline
    1903966 & Management of baldness \\ \hline
    38088660 & Management of androgenic alopecia \\ \hline
    1503105 & Jayne Torvill \\ \hline
    1503115 & Christopher Dean \\ \hline
    184843 & Henry VI, Part 1 \\ \hline
    184846 & Henry VI, Part 2 \\ \hline
    184847 & Henry VI, Part 3 \\ \hline
    10701462 & List of birds of Zambia \\ \hline
    10930255 & List of birds of Zimbabwe \\ \hline
    10930111 & List of birds of Mozambique \\ \hline
    48711 & Oregon Trail \\ \hline
    31518964 & History of the Oregon Trail \\
    \hline
\end{tabular}
\end{table}

>>>>

\documentclass{acm_proc_article-sp}
\usepackage{url}
\usepackage{algpseudocode}
\usepackage{verbatim}
\usepackage{microtype}
\usepackage{enumerate}
\usepackage{enumitem}
\usepackage{epsfig}
\usepackage{algorithmicx}
\usepackage{algorithm}
\usepackage{natbib}
\usepackage[utf8]{inputenc}
\begin{document}

@@

Based on our preliminary analysis, templatification tends to occur most often between articles that maintain large lists of information related to the same general sub-theme of different topics. For example, the articles ''List of birds of Zambia'' and ''List of birds of Tanzania'' share a large number of templated sentences. With both countries sharing the same geographic region, it is not unexpected that their respective Wikipedia articles on the countrys' bird species would be highly comparable. For clarity purposes, we define \emph{similarity count} as simply the total number of sentences between two articles that were found to share the same hash signature. Using the output of the minhashing routine, we performed a pairwise similarity count across all articles that shared similar sentences. Overall, we found $\approx 29580$ wikipedia article pairs that had a similarity count greater than $50$.

@@

\begin{table}
\centering
\caption{Top 10 Article Pair Titles}
{\small
\begin{tabular}{| l |}
    \hline
\{Private equity in the 2000s, History of private equity and venture capital, Private equity in the 1980s\} \\
\{List of ethnic cleansings, Ethnic cleansing\} \\
\{Route of the Oregon Trail, Oregon Trail\} \\
\{English literature, British literature\} \\
\{Portia schultzi, Portia labiata, Portia fimbriata\} \\
\{Lesbian American history, List of lesbian, gay, bisexual, or transgender firsts by year\} \\
\{Lists of British inventions, List of English inventions and discoveries\} \\
\{1981 in baseball, 1981 Major League Baseball season\} \\
\{Minority Report (film), Themes in Minority Report\} \\
\{What Is History?, E. H. Carr\} \\
\{Individualist anarchism in Europe, Individualist anarchism in the United States, Individualist anarchism, Anarchism in the United States\} \\
\{Kingdom of Scotland, Scotland in the Early Modern Era\} \\
\{Decline of Greco-Roman polytheism, Christian persecution of paganism after Theodosius I until the fall of the Roman Empire\} \\
\{Anarchist schools of thought, Libertarian socialism, Anarchist communism, Anarchism, History of anarchism, Libertarian Marxism\} \\
\{Brill Tramway, Quainton Road railway station\} \\
\{History of the Roman Empire, Byzantine Empire, History of the Byzantine Empire\} \\
\{List of American state and local politicians convicted of crimes, List of state and local political scandals in the United States\} \\
\{Filioque, History of the Filioque controversy\} \\
\{1960 Major League Baseball season, 1960 in baseball\} \\
\{Domitian, Flavian dynasty\} \\
\{Military history of Australia during World War II, Australian Army during World War II\} \\
\{Kuomintang, History of the Kuomintang\} \\
\{Interracial marriage, Miscegenation, Eurasian (mixed ancestry)\} \\
\{Scotland in the modern era, History of Scotland\} \\
\{History of California, Maritime history of California\} \\
\{Outline of project management, Glossary of project management\} \\
\{Wigan Warriors, History of Wigan Warriors\} \\
\{List of American federal politicians convicted of crimes, List of federal political scandals in the United States\} \\
\{Economy of England in the Middle Ages, Economics of English towns and trade in the Middle Ages\} \\
\{Galvatron, Megatron\} \\
\{Metropolitan Police role in the news media phone hacking scandal, News media phone hacking scandal\} \\
\{List of Shakespearean characters (L-Z), List of Shakespearean characters (A-K), List of historical figures dramatised by Shakespeare\} \\
\{Fetal alcohol spectrum disorder, Fetal alcohol syndrome\} \\
\{List of marine bony fishes of South Africa, List of marine animals of the Cape Peninsula and False Bay\} \\
\{History of painting, Western painting, 20th-century Western painting\} \\
\{Timeline of the 2007 Burmese anti-government protests, 2007 Burmese anti-government protests\} \\
\{Precipitation, Rain\} \\
\{List of Puerto Ricans, List of Puerto Rican military personnel\} \\
\{Glossary of basketball terms, Outline of basketball\} \\
\{Hannibal, Conquests of Hannibal\} \\
\{Bogotá, History of Bogotá\} \\
\{Pseudotsuga menziesii var. menziesii, Douglas fir\} \\
\{History of the East-West Schism, East-West Schism\} \\
\{List of attacks in Lebanon, Lebanon bombings and assassinations (2004-present)\} \\
\{Zen, Chinese Chán\} \\
\{List of Deadliest Warrior episodes, Deadliest Warrior (season 1), Deadliest Warrior (season 3), Deadliest Warrior (season 2)\} \\
\{1991 Major League Baseball season, 1991 in baseball\} \\
\{American rock, Rock music\} \\
\{Test matches in England in 2005, Australian cricket team in England in 2005\} \\
\{Swedes, Sweden\} \\
\{Glossary of robotics, Outline of robotics\} \\
\{CIA leak scandal criminal investigation, Plame affair grand jury investigation\} \\
\{History of Australia since 1945, History of Australia\} \\
\{List of Russian people, List of Russian scientists\} \\
    %% 21986867 & 2000 New Year Honours \\ \hline
    %% 21986897 & 1999 New Year Honours \\ \hline
    %% 3951586 & Instruments of the United Kingdom, 1994 \\ \hline
    %% 3951664 & Instruments of the United Kingdom, 1995 \\ \hline
    %% 1903966 & Management of baldness \\ \hline
    %% 38088660 & Management of androgenic alopecia \\ \hline
    %% 1503105 & Jayne Torvill \\ \hline
    %% 1503115 & Christopher Dean \\ \hline
    %% 184843 & Henry VI, Part 1 \\ \hline
    %% 184846 & Henry VI, Part 2 \\ \hline
    %% 184847 & Henry VI, Part 3 \\ \hline
    %% 10701462 & List of birds of Zambia \\ \hline
    %% 10930255 & List of birds of Zimbabwe \\ \hline
    %% 10930111 & List of birds of Mozambique \\ \hline
    %% 48711 & Oregon Trail \\ \hline
    %% 31518964 & History of the Oregon Trail \\
    \hline
\end{tabular}
}
\end{table}
